---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r}
options(scipen = 1)
```

## Loading and preprocessing the data

```{r loaddata}
data<-read.csv("activity.csv", stringsAsFactors=FALSE)
```

## What is mean total number of steps taken per day?

```{r meantotal}
databyday<-aggregate(steps ~ date, data=data, FUN="sum")
with (databyday,
      hist(steps)
)
mean<-mean(databyday$steps)
median<-median(databyday$steps)
#Then use `r round(mean,2)` and `r median`
```

Mean: `r round(mean,2)`

Median: `r median`

## What is the average daily activity pattern?

```{r acrossdays}
databyinterval<-aggregate(steps ~ interval, data=data, FUN="mean")
with (databyinterval,
      plot(interval, steps, type='l')
)
busiestinterval<-databyinterval[which.max(databyinterval$steps),]
#Then use `r busiestinterval[1]` and `r round(busiestinterval[2],2)`
```

The interval with the most steps on average is `r busiestinterval[1]` with `r round(busiestinterval[2],2)` steps.

## Imputing missing values

```{r missingvals}
numbermissing<-sum(is.na(data$steps))
#Then use `r numbermissing`

datanasreplaced<-data[is.na(data)]<-
```

There are `r numbermissing` rows with 'NA' steps

## Are there differences in activity patterns between weekdays and weekends?
